### 2016-07-29 hoist.tex
adding topics

\section{Cost models}
\subsection{In the presence of calls}
\subsection{Hoisting too far away}

\section{Comparative analysis of different approaches to hoisting}
\subsection{Optimistic approach}
Collect GVN of all the instructions in the beginning.
\subsection{Pessimistic approach}
Start from a branch.

>>>>

\section{Cost models}
\subsection{In the presence of calls}
Hoisting scalars across calls is tricky because it can increase the number of spills.

\subsection{Hoisting too far away}
\begin{enumerate}
\item When the hoist point is too far.
\item When the number of instructions we may cross is very high.
\end{enumerate}

\section{Comparative analysis of different approaches to hoisting}
\subsection{Optimistic approach}
Collect GVN of all the instructions in the beginning.
\subsection{Pessimistic approach}
Start from a branch. Hoist one by one iteratively.
\subsection{Triangle approach}

\section{Using MemorySSA}
\subsection{Iterative update to memory ssa during the hoisting process}

\section{Without MemorySSA using the dominance information}
